SimBio: a flexible and extensible Python package for systems modelling

### 2023-11-10 article.qmd
Explain the symbolite backends

Symbolite is a lightweight symbolics package to create algebraic mathematical expressions.
They can be inspected and compiled to different backends.
Currently, we have implementations for NumPy (and Numba), SymPy and JAX,
but it is easy to add new backends.

>>>>

Symbolite is a lightweight symbolics package to create algebraic mathematical expressions.
They can be inspected and compiled to different backends.
Currently, we have implementations for
NumPy [@harrisArrayProgrammingNumPy2020];
Numba [@lamNumbaLLVMbasedPython2015], a Just-in-Time (JIT) compiler to LLVM;
SymPy [@meurerSymPySymbolicComputing2017], a library for symbolic mathematics;
and JAX [@jax2018github], a library that support automatic differentation
and compilation to GPUs and TPUs;
but it is easy to add new backends.
